---
title: "MONIA Analysis report"
always_allow_html: yes
params: null
---
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(DT)
library(dplyr)
library(kableExtra)
library(knitr)
library(networkD3)
library(htmlwidgets)
```

<style>
h1, h2, h3, h4 {
  color:#17247a;
}
</style>

## Model performances

```{r diabloFeat, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}

featDiablo <- getClassif(obj, method= "diablo", result = "featDetails")
if (length(featDiablo) > 0 )
{ 

    cat("### Diablo model \n")
    
    cat("Diablo **sPLS-DA** method selects a relevant features subset to 
        classification performance and correlation values. These features
        could be used in functional enrichment analysis to further analysis 
        provide by *MONIA*. \n")
    cat("\n#### Features selected for each omic dataset \n ")
    
    i = 1
    while (i <= length(featDiablo))
    {
        df <- featDiablo[[i]][[1]]$data
        caption <- paste0("Omic", i, ": Features selected by Diablo - sPLS-DA 
                          method")
        tbl <- kbl(df, digits = 4, format = "simple", caption = caption)
        print(tbl)
        
        i = i + 1
    }
    cat("\n#### sPLS-DA performances \n ")
}else
{
    cat("### Diablo model not computed \n")
}
```

```{r diabloPerf, echo=FALSE, message=FALSE, warning=FALSE}
perfDiablo <- getClassif(obj, method = "diablo", result = "performance")
if (length(perfDiablo) > 0 )
{
  print(perfDiablo)
}
```


```{r biosignerFeat, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}

# featBiosigner <- obj$classification$biosignerResult$featDetails
featBiosigner <- getClassif(obj, method= "biosigner", result = "featDetails")

if (length(featBiosigner) > 0 )
{ 

    cat("### Biosigner model \n")
    
    cat("Biosigner method selects a small statistical significative features
    subset to classification performance. 
\n")
    cat("#### Features selected for each omic dataset \n ")
  
    i <- 1
    while (i <= length(featBiosigner))
    {
        df <- featBiosigner[[i]][[1]]$data
        caption <- paste0("Omic", i, ": Features selected by Biosigner 
        (SVM & RF) method")
        tbl <- kbl(df, digits = 4, format = "simple", caption = caption)
        print(tbl)
        
        i <- i + 1
    }
    cat("\n#### Biosigner performances \n ")
}else
{
    cat("### Biosigner model not computed \n")
}
```

```{r echo=FALSE, message=TRUE, warning=TRUE}
# perfBiosigner <- obj$classification$biosignerResult$performance
perfBiosigner <- getClassif(method = "biosigner", result = "performance")

if (length(perfBiosigner) > 0 )
{
    print(perfBiosigner)
}

```


## Enrichment analysis

Functional enrichment analysis have been computed with Diablo subsets of 
features. You could retrieve "*single-omic*" results and *"multi-omic"* below.
A Stouffer's p-value is a p-values pooling result weighted or not by number of
features used to identify at least one biological elements for each omic data.  

```{r results='asis', echo=FALSE, message=TRUE, warning=TRUE}
# dataNames <- names(obj$enrichment$diablo$featureConverted)
convFeat <- getEnrichment(obj, sourceFeat = "diablo", 
                          infoType = "featureConverted")
dataNames <- names(convFeat)

enrichResPathways <- getEnrichment(obj, sourceFeat = "diablo", 
                          infoType = "pathways")
enrichResGO <- getEnrichment(obj, sourceFeat = "diablo", 
                          infoType = "go")
# enrichResPathways <- obj$enrichment$diablo$pathways
# enrichResGO <- obj$enrichment$diablo$go
```

### Pathways

```{r enrichmentResultPathways, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}
if (length(enrichResPathways) > 0)
{
    i <- 1
    while(i <= length(enrichResPathways))
    {
        db <- enrichResPathways[[i]]$result
        j <- 1
        cat(paste0("\n <br><div style = 'display: inline-block;
        vertical-align:middle; width: 100%; text-align: center;'><h4>",  
        names(enrichResPathways)[i], "</h4></div> \n"))
                  
                   # "</h1> \n"))
        # cat("\n \\subsection{", names(enrichResPathways)[i], "} \n")
        while (j <= length(db))
        {
            cat("\n \\subsubsection{Enrichment results for Omic", j, "} \n")
            if (j <= length(dataNames)) # Single omic enrichment table
            {
                ## load a small part of table
                t <- db[[j]][seq(1, 10),  seq(1, 7)]
                t$ID <- addEnrichIDUrl(t$ID, names(enrichResPathways)[i])
                
                table <- t %>% 
                  kbl(digits = 4, row.names = FALSE, format = "simple", 
                    caption = paste0(names(enrichResPathways)[i], 
                                     " - Enrichment result table for Omic", 
                                     j))
                
                print(table)
            }
            else if (j == length(dataNames) + 1 ) ## Stouffer table
            {
                cat("\n \\subsubsection{Multi-Omic 
                    enrichment analysis with Stouffer's p-value}\n")
        
                ## load a small part of table
                # t <- db[[j]][c(seq(1, 6), seq(8, 10)), ]
                t <- db[[j]][seq(1, 10), ] %>% select(everything(), -geneID)
                t$ID <- addEnrichIDUrl(t$ID, names(enrichResPathways)[i]) 
                
                table <- t %>% 
                    kbl(digits = 4, 
                        row.names = FALSE, 
                        format = "simple", 
                        caption = paste0(names(enrichResPathways)[i], 
                                         " - Multi-omic enrichment table"))
                print(table)
            }
            else if (j == length(dataNames) + 2) ## enrichment Map
            {
              cat("\n \\subsubsection{Multi-Omic 
                    enrichment map with Stouffer's p-value <= 0.1}\n")
              print(db[[j]])
            }
            j = j + 1
        }
        i = i + 1
    }
}else{
  cat("No pathways enrichment result \n")
}
```

### Gene Ontology
```{r enrichmentResultGO, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}

if (length(enrichResGO) > 0)
{
    i = 1
    while(i <= length(enrichResGO))
    {
        db <- enrichResGO[[i]]
        j = 1
        cat(paste0("\n <br><div style = 'display: inline-block;
        vertical-align:middle; width: 100%; text-align: center;'><h4>",  
        names(enrichResGO)[i], "</h4></div> \n"))
        # cat("\n \\subsection{", names(enrichResGO)[i], "}\n \\ ")
        while (j <= length(db))
        {
            cat("\n \\subsubsection{Enrichment results for Omic", j, "}\n")
            if (j <= length(dataNames)) # Single omic enrichment table
            {
                ## load a small part of table
                t <- db[[j]][seq(1, 10), seq(1, 7)]
                t$ID <- addEnrichIDUrl(t$ID, names(enrichResGO)[i]) 
                
                ## displays table
                table <- t %>%
                kbl(digits = 4, 
                    row.names = FALSE, 
                    format = "simple",
                    caption = paste0(names(enrichResGO)[i], 
                                     " - Enrichment result table for Omic", 
                                     j))
                print(table)
            }
            else if (j == length(dataNames) + 1 ) ## Stouffer table
            {
                cat("\n \\subsubsection{Multi-Omic 
                    enrichment analysis with Stouffer's p-value}\n")
        
                ## load a small part of table
                t <- db[[j]][seq(1, 10), ] %>% select(everything(), -geneID)
                t$ID <- addEnrichIDUrl(t$ID, names(enrichResGO)[i]) 
                
                table <- t %>% kbl(digits = 4, 
                        row.names = FALSE, 
                        format = "simple", 
                        caption = paste0(names(enrichResGO)[i],
                                         " - Multi-omic enrichment table"))
                print(table)
            }
            else if (j == length(dataNames) + 2) ## enrichment Map
            {
              cat("\n \\subsubsection{Multi-Omic 
                    enrichment map with Stouffer's p-value <= 0.1}\n")
              print(db[[j]])
            }
            j = j + 1
        }
        i = i + 1
    }
}else{
  cat("No ontology enrichment result \n")
}

```

## Multi-Omic Network inference

Several network analysis methods are used by *MONIA*. You can retrieve 
correlation, partial correlation and mutual information networks whose 
relevancy to improve relevant relation identification between numerical values
have been shown in [**Hawe, Johann S. and Theis, Fabian J. and Heinig, Matthias, 2019**](https://www.frontiersin.org/articles/10.3389/fgene.2019.00535/full).

### Diablo features networks

#### Correlation network
```{r correlationNetworkDiablo, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}

if (length(getNetwork(obj, "diablo")) > 0)
{
    # corrNet <- obj$networkInference$diabloNetwork$graph$correlation
    corrNet <- getNetwork(obj, "diablo", "correlation")
    if (!is.null(corrNet))
    {
        onRender(corrNet,
          "function(el,x)
              { d3.selectAll('.node').on('mouseover', null); }")
    }else
    {
        cat("<i>Network picture not loaded in app</i>")
    }
}else{
    cat("<i>No diablo networks loaded or computed</i> \n")
}
```

#### Partial correlation network
```{r partialCorrNetworkInferenceDiablo, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}
if (length(getNetwork(obj, "diablo")) > 0)
{
    # pcorrNet <- obj$networkInference$diabloNetwork$graph$partialCorrelation
    pcorrNet <- getNetwork(obj, "diablo", "partialCor")
    if (!is.null(pcorrNet))
    {
        onRender(pcorrNet,
            "function(el,x)
                { d3.selectAll('.node').on('mouseover', null); }")
    }else{
        cat("<i>Network picture not loaded in app</i>")
    }
}else
{
    cat("<i>No diablo networks loaded or computed</i> \n")
}
```

#### Mutual information network
```{r mutualInfNetworkInferenceDiablo, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}
if (length(getNetwork(obj, "diablo")) > 0)
{
    # imNet <- obj$networkInference$diabloNetwork$graph$mutualInformation
    imNet <- getNetwork(obj, "diablo", "mutualInf")
    if (!is.null(imNet))
    {
        onRender(imNet,
            "function(el,x)
                { d3.selectAll('.node').on('mouseover', null); }")
    }else{
        cat("<i>Network picture not loaded in app</i>")
    }
}else{
    cat("<i>No diablo networks loaded or computed</i> \n")
}
cat("\n <hr style='height: 50px; width: 100% ;
    color: #f1f1f1; background-color: #f1f1f1;'> \n")

```


### Biosigner features networks

#### Correlation network
```{r correlationNetworkBiosigner, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}

if (length(getNetwork(obj, "biosigner")) > 0)
{
  # corrNet <- obj$networkInference$biosignerNetwork$graph$correlation
  corrNet <- getNetwork(obj, "biosigner", "correlation")
  if (!is.null(corrNet))
  {
    onRender(corrNet,
        "function(el,x)
            { d3.selectAll('.node').on('mouseover', null); }")
  }else{
      cat("<i>Network picture not loaded in app</i>")
  }
}else{
  cat ("<i>No biosigner networks loaded or computed</i> \n")
}
```

#### Partial correlation network
```{r partialCorrNetworkInferenceBiosigner, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}
if (length(getNetwork(obj, "biosigner")) > 0)
{
  # pcorrNet <- obj$networkInference$biosignerNetwork$graph$partialCorrelation
  pcorrNet <- getNetwork(obj, "biosigner", "partialCor")
  if (!is.null(pcorrNet))
  {
      onRender(pcorrNet,
      "function(el,x)
          { d3.selectAll('.node').on('mouseover', null); }")
  }else{
      cat("<i>Network picture not loaded in app</i>")
  }
}else{
    cat("<i>No biosigner networks loaded or computed</i> \n")
}
```

#### Mutual information network
```{r mutualInfNetworkInferenceBiosigner, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}
if (length(getNetwork(obj, "biosigner")) > 0)
{
    # miNet <- obj$networkInference$biosignerNetwork$graph$mutualInformation
    miNet <- getNetwork(obj, "biosigner", "mutualInf")
    if (!is.null(miNet))
    {
        onRender(miNet,
        "function(el,x)
            { d3.selectAll('.node').on('mouseover', null); }")
    }else{
        cat("<i>Network picture not loaded in app</i>")
    }
}else{
    cat("<i>No biosigner networks loaded or computed</i> \n")
}
cat("\n <hr style='height: 50px; width: 100% ;
    color: #f1f1f1; background-color: #f1f1f1;'> \n")

```

## Bibliographic assumptions
```{r biblioDiablo, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}
if (length(obj$networkInference$diabloNetwork$biblio) > 0)
{
  cat("<h3>Diablo features | Bibliographic query: \n</h3>", 
      getPubMed(obj, "diablo", "request")
  )
  titles_urls <- getPubMed(obj, "diablo", "all")
  i <- 1
  while (i <=  length(titles_urls$title))
  {
    title <- titles_urls$title[[i]]
    url <- titles_urls$url[[i]]
    cat("<li><a href = ", url, "> ", title, "</a></li>\n")
    i <- i + 1
  }
}
```

```{r biblioBiosigner, results = 'asis', fig.align='center', fig.pos='htb!', echo=FALSE, message=FALSE, warning=FALSE}
if (length(obj$networkInference$biosignerNetwork$biblio) > 0)
{
    cat("<h3>Biosigner features | Bibliographic query:</h3>", 
        getPubMed(obj, "biosigner", "request"))
    titles_urls <- getPubMed(obj, "biosigner", "all")
    i <- 1
    while (i <=  length(titles_urls$title))
    {
        title <- titles_urls$title[[i]]
        url <- titles_urls$url[[i]]
        cat("<li><a href = ", url, "> ", title, "</a></li>")
        i <- i + 1
    }
}
cat("\n <hr style='height: 50px; width: 100% ;
    color: #f1f1f1; background-color: #f1f1f1;'> \n")

```


